---
title: "Simulated Data"
author: "Jack Nowacek"
date: "2023-06-20"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Package Prep and Library

```{r packages, warning=FALSE}
library(Distance)
library(mrds)
library(dsims)
library(sf)
library(dssd)
library(knitr)
library(tidyverse)
library(reshape)
library(ggplot2)
library(pbapply)
#install.packages("devtools")
 library(devtools)
  #install_github("DistanceDevelopment/dssd", build_vignettes = TRUE)
  #install_github("DistanceDevelopment/dsims", build_vignettes = TRUE)
```

Working with Dsims creating the region for study

This creates a 3000 by 2000 meter region which we can add a population distribution to, creating a functional study area. Below is a plot of the region with no population.

```{r study area specifications}
# Find the file path to the example shapefile in dssd
#shapefile.name <- system.file("extdata", "StAndrew.shp", package = "dssd")

study_area <- matrix(c(0, 0, 3000, 0, 3000, 2000, 0, 2000, 0, 0), ncol = 2, byrow = TRUE)
study_area_data <- data.frame(ID = 1)
study_area_sf <- st_sf(geometry =  
            st_sfc(st_polygon(list(study_area))), data = study_area_data)

print(study_area_sf)
# Create the survey region object
region <- make.region(region.name = "Test Area",
                      shape = study_area_sf,
                      units = "m")
plot(region)
```

This chunk adds a uniform population density to the study area, allowing us to perform analysis on the study area. Below is a density plot of our study region, the uniform color corresponds to the uniform population distribution.

```{r density over study area}
# We first create a flat density grid
density <- make.density(region = region,
                        x.space = 100,
                        y.space = 100,
                        constant = 1)

plot(density, region, scale = 1)
```

This chunk turns our uniform density into a dataset, allowing us to see its raw form. This raw data would be similar to data that we may collect on line transect surverys.

```{r create dataset for density over area}
density.data <- density@density.surface[[1]]
head(density.data)
```

This chunk defines the population distribution. First, the covariates are defined, in our case, group size. The group size in this data averages 2 and follows a zero-truncated Poissant distribution. This group size distribution is fed into the model along with the region and population density that we defined previously. Here we also specify our population size, in number of groups.

```{r group size covariance distribution}
 # Create a covariate list describing the distribution of cluster sizes
 s <- 20
 #covariates <- list(size = list(distribution = "ztruncpois", mean = s))

 covariate.list <- list()
 covariate.list$size <- list(list(distribution = "ztruncpois", mean = s))

 # Define the population description
 pop.desc <- make.population.description(region = region,
                                         density = density,
                                         covariates = covariate.list,
                                         N = 500,
                                         fixed.N = TRUE)
```

Here we define our detection function by defining our scale parameter and our truncation distance. 

```{r detection function}

# test values for beta_0: 4, 5, 6, 7 ,8
#test values for beta_1: .052, .053, .054, .055, .056

beta_0_11 <- 4
beta_1_11 <- 0.052

beta_0_12 <- 4
beta_1_12 <- 0.053

beta_0_13 <- 4
beta_1_13 <- 0.054

beta_0_14 <- 4
beta_1_14 <- 0.055

beta_0_15 <- 4
beta_1_15 <- 0.056

beta_0_21 <- 5
beta_1_21 <- 0.052

beta_0_22 <- 5
beta_1_22 <- 0.053

beta_0_23 <- 5
beta_1_23 <- 0.054

beta_0_24 <- 5
beta_1_24 <- 0.055

beta_0_25 <- 5
beta_1_25 <- 0.056

beta_0_31 <- 6
beta_1_31 <- 0.052

beta_0_32 <- 6
beta_1_32 <- 0.053

beta_0_33 <- 6
beta_1_33 <- 0.054

beta_0_34 <- 6
beta_1_34 <- 0.055

beta_0_35 <- 6
beta_1_35 <- 0.056

beta_0_41 <- 7
beta_1_41 <- 0.052

beta_0_42 <- 7
beta_1_42 <- 0.053

beta_0_43 <- 7
beta_1_43 <- 0.054

beta_0_44 <- 7
beta_1_44 <- 0.055

beta_0_45 <- 7
beta_1_45 <- 0.056

beta_0_51 <- 8
beta_1_51 <- 0.052

beta_0_52 <- 8
beta_1_52 <- 0.053

beta_0_53 <- 8
beta_1_53 <- 0.054

beta_0_54 <- 8
beta_1_54 <- 0.055

beta_0_55 <- 8
beta_1_55 <- 0.056

w <- 100

detect.hn_11 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_11, 
                                cov.param = list(size = beta_1_11),
                                truncation = w)

detect.hn_12 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_12, 
                                cov.param = list(size = beta_1_12),
                                truncation = w)

detect.hn_13 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_13, 
                                cov.param =list(size =  beta_1_13),
                                truncation = w)

detect.hn_14 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_14, 
                                cov.param = list(size = beta_1_14),
                                truncation = w)

detect.hn_15 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_15, 
                                cov.param = list(size = beta_1_15),
                                truncation = w)

detect.hn_21 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_21, 
                                cov.param = list(size = beta_1_21),
                                truncation = w)

detect.hn_22 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_22, 
                                cov.param = list(size = beta_1_22),
                                truncation = w)

detect.hn_23 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_23, 
                                cov.param = list(size = beta_1_23),
                                truncation = w)

detect.hn_24 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_24, 
                                cov.param = list(size = beta_1_24),
                                truncation = w)

detect.hn_25 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_25, 
                                cov.param = list(size = beta_1_25),
                                truncation = w)

detect.hn_31 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_31, 
                                cov.param = list(size = beta_1_31),
                                truncation = w)

detect.hn_32 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_32, 
                                cov.param = list(size = beta_1_32),
                                truncation = w)

detect.hn_33 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_33, 
                                cov.param = list(size = beta_1_33),
                                truncation = w)

detect.hn_34 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_34, 
                                cov.param = list(size = beta_1_34),
                                truncation = w)

detect.hn_35 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_35, 
                                cov.param = list(size = beta_1_35),
                                truncation = w)

detect.hn_41 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_41, 
                                cov.param = list(size = beta_1_41),
                                truncation = w)

detect.hn_42 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_42, 
                                cov.param = list(size = beta_1_42),
                                truncation = w)

detect.hn_43 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_43, 
                                cov.param = list(size = beta_1_43),
                                truncation = w)

detect.hn_44 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_44, 
                                cov.param = list(size = beta_1_44),
                                truncation = w)

detect.hn_45 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_45, 
                                cov.param =list(size =  beta_1_45),
                                truncation = w)

detect.hn_51 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_51, 
                                cov.param = list(size = beta_1_51),
                                truncation = w)

detect.hn_52 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_52, 
                                cov.param = list(size = beta_1_52),
                                truncation = w)

detect.hn_53 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_53, 
                                cov.param = list(size = beta_1_53),
                                truncation = w)

detect.hn_54 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_54, 
                                cov.param = list(size = beta_1_54),
                                truncation = w)

detect.hn_55 <- make.detectability(key.function = "hn", 
                                scale.param = beta_0_55, 
                                cov.param = list(size = beta_1_55),
                                truncation = w)
# We can now visualise these detection functions
plot(detect.hn_33, pop.desc)
```

Here we define our survey design as a line transect survey with systematic (parallel) lines. We define our spacing between survey lines and again our truncation distance. The plot below lets us visualize the survey tracks.

A note on truncation distance: while we can define our truncation distance in multiple places, note the effective truncation distance from the detection function.


```{r survey design}
# Define the design
design <- make.design(region = region,
                      transect.type = "line",
                      design = "systematic",
                      spacing = 300,
                      truncation = 100)
```

```{r plot of transects}
transects <- generate.transects(design)
plot(region, transects)
```

The next two code chunks define our analyses and simulations, using our survey design, population description, and detection function. The four results tables are a map of the transects through the study area, a map of the population on the study area, a third plot with both of the previous elements, displaying the groups which were detected, and finally the detection increment histogram.

```{r analysis specifications}
ds.analyses_standard <- make.ds.analysis(dfmodel = list(~1),
                                key = c("hn"),
                                truncation = 100,
                                criteria = "AIC")

ds.analyses_size_cov <- make.ds.analysis(dfmodel = list(~size),
                                key = c("hn"),
                                truncation = 100,
                                criteria = "AIC")
```

```{r simulation design standard}
sim_11_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_11,
                       ds.analysis = ds.analyses_standard)

sim_12_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_12,
                       ds.analysis = ds.analyses_standard)

sim_13_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_13,
                       ds.analysis = ds.analyses_standard)

sim_14_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_14,
                       ds.analysis = ds.analyses_standard)

sim_15_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_15,
                       ds.analysis = ds.analyses_standard)

sim_21_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_21,
                       ds.analysis = ds.analyses_standard)

sim_22_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_22,
                       ds.analysis = ds.analyses_standard)

sim_23_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_23,
                       ds.analysis = ds.analyses_standard)

sim_24_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_24,
                       ds.analysis = ds.analyses_standard)

sim_25_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_25,
                       ds.analysis = ds.analyses_standard)

sim_31_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_31,
                       ds.analysis = ds.analyses_standard)

sim_32_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_32,
                       ds.analysis = ds.analyses_standard)


sim_33_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_33,
                       ds.analysis = ds.analyses_standard)

sim_34_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_34,
                       ds.analysis = ds.analyses_standard)

sim_35_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_35,
                       ds.analysis = ds.analyses_standard)

sim_41_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_41,
                       ds.analysis = ds.analyses_standard)

sim_42_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_42,
                       ds.analysis = ds.analyses_standard)

sim_43_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_43,
                       ds.analysis = ds.analyses_standard)

sim_44_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_44,
                       ds.analysis = ds.analyses_standard)

sim_45_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_45,
                       ds.analysis = ds.analyses_standard)

sim_51_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_51,
                       ds.analysis = ds.analyses_standard)

sim_52_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_52,
                       ds.analysis = ds.analyses_standard)

sim_53_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_53,
                       ds.analysis = ds.analyses_standard)

sim_54_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_54,
                       ds.analysis = ds.analyses_standard)

sim_55_standard <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_55,
                       ds.analysis = ds.analyses_standard)

```

```{r simulation design size covariate}
sim_11_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_11,
                       ds.analysis = ds.analyses_size_cov)

sim_12_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_12,
                       ds.analysis = ds.analyses_size_cov)

sim_13_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_13,
                       ds.analysis = ds.analyses_size_cov)

sim_14_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_14,
                       ds.analysis = ds.analyses_size_cov)

sim_15_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_15,
                       ds.analysis = ds.analyses_size_cov)

sim_21_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_21,
                       ds.analysis = ds.analyses_size_cov)

sim_22_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_22,
                       ds.analysis = ds.analyses_size_cov)

sim_23_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_23,
                       ds.analysis = ds.analyses_size_cov)

sim_24_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_24,
                       ds.analysis = ds.analyses_size_cov)

sim_25_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_25,
                       ds.analysis = ds.analyses_size_cov)

sim_31_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_31,
                       ds.analysis = ds.analyses_size_cov)

sim_32_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_32,
                       ds.analysis = ds.analyses_size_cov)


sim_33_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_33,
                       ds.analysis = ds.analyses_size_cov)

sim_34_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_34,
                       ds.analysis = ds.analyses_size_cov)

sim_35_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_35,
                       ds.analysis = ds.analyses_size_cov)

sim_41_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_41,
                       ds.analysis = ds.analyses_size_cov)

sim_42_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_42,
                       ds.analysis = ds.analyses_size_cov)

sim_43_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_43,
                       ds.analysis = ds.analyses_size_cov)

sim_44_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_44,
                       ds.analysis = ds.analyses_size_cov)

sim_45_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_45,
                       ds.analysis = ds.analyses_size_cov)

sim_51_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_51,
                       ds.analysis = ds.analyses_size_cov)

sim_52_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_52,
                       ds.analysis = ds.analyses_size_cov)

sim_53_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_53,
                       ds.analysis = ds.analyses_size_cov)

sim_54_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_54,
                       ds.analysis = ds.analyses_size_cov)

sim_55_size_cov <- make.simulation(reps = 3, 
                       design = design,
                       population.description = pop.desc,
                       detectability = detect.hn_55,
                       ds.analysis = ds.analyses_size_cov)
```

The tables below summarize our statistical results. This final plot provides a histogram of the population estimates from each simulation. 

```{r standard simulations}
sim_11_standard <- 
  run.simulation(simulation = sim_11_standard, run.parallel = TRUE)
sim_12_standard <- 
  run.simulation(simulation = sim_12_standard, run.parallel = TRUE)
sim_13_standard <- 
  run.simulation(simulation = sim_13_standard, run.parallel = TRUE)
sim_14_standard <- 
  run.simulation(simulation = sim_14_standard, run.parallel = TRUE)
sim_15_standard <- 
  run.simulation(simulation = sim_15_standard, run.parallel = TRUE)
sim_21_standard <- 
  run.simulation(simulation = sim_21_standard, run.parallel = TRUE)
sim_22_standard <- 
  run.simulation(simulation = sim_22_standard, run.parallel = TRUE)
sim_23_standard <- 
  run.simulation(simulation = sim_23_standard, run.parallel = TRUE)
sim_24_standard <- 
  run.simulation(simulation = sim_24_standard, run.parallel = TRUE)
sim_25_standard <- 
  run.simulation(simulation = sim_25_standard, run.parallel = TRUE)
sim_31_standard <- 
  run.simulation(simulation = sim_31_standard, run.parallel = TRUE)
sim_32_standard <- 
  run.simulation(simulation = sim_32_standard, run.parallel = TRUE)
sim_33_standard <- 
  run.simulation(simulation = sim_33_standard, run.parallel = TRUE)
sim_34_standard <- 
  run.simulation(simulation = sim_34_standard, run.parallel = TRUE)
sim_35_standard <- 
  run.simulation(simulation = sim_35_standard, run.parallel = TRUE)
sim_41_standard <- 
  run.simulation(simulation = sim_41_standard, run.parallel = TRUE)
sim_42_standard <- 
  run.simulation(simulation = sim_42_standard, run.parallel = TRUE)
sim_43_standard <- 
  run.simulation(simulation = sim_43_standard, run.parallel = TRUE)
sim_44_standard <- 
  run.simulation(simulation = sim_44_standard, run.parallel = TRUE)
sim_45_standard <- 
  run.simulation(simulation = sim_45_standard, run.parallel = TRUE)
sim_51_standard <- 
  run.simulation(simulation = sim_51_standard, run.parallel = TRUE)
sim_52_standard <- 
  run.simulation(simulation = sim_52_standard, run.parallel = TRUE)
sim_53_standard <- 
  run.simulation(simulation = sim_53_standard, run.parallel = TRUE)
sim_54_standard <- 
  run.simulation(simulation = sim_54_standard, run.parallel = TRUE)
sim_55_standard <- 
  run.simulation(simulation = sim_55_standard, run.parallel = TRUE)
```

```{r size covariate simulations}
sim_11_size_cov <- 
  run.simulation(simulation = sim_11_size_cov, run.parallel = TRUE)
sim_12_size_cov <- 
  run.simulation(simulation = sim_12_size_cov, run.parallel = TRUE)
sim_13_size_cov <- 
  run.simulation(simulation = sim_13_size_cov, run.parallel = TRUE)
sim_14_size_cov <- 
  run.simulation(simulation = sim_14_size_cov, run.parallel = TRUE)
sim_15_size_cov <- 
  run.simulation(simulation = sim_15_size_cov, run.parallel = TRUE)
sim_21_size_cov <- 
  run.simulation(simulation = sim_21_size_cov, run.parallel = TRUE)
sim_22_size_cov <- 
  run.simulation(simulation = sim_22_size_cov, run.parallel = TRUE)
sim_23_size_cov <- 
  run.simulation(simulation = sim_23_size_cov, run.parallel = TRUE)
sim_24_size_cov <- 
  run.simulation(simulation = sim_24_size_cov, run.parallel = TRUE)
sim_25_size_cov <- 
  run.simulation(simulation = sim_25_size_cov, run.parallel = TRUE)
sim_31_size_cov <- 
  run.simulation(simulation = sim_31_size_cov, run.parallel = TRUE)
sim_32_size_cov <- 
  run.simulation(simulation = sim_32_size_cov, run.parallel = TRUE)
sim_33_size_cov <- 
  run.simulation(simulation = sim_33_size_cov, run.parallel = TRUE)
sim_34_size_cov <- 
  run.simulation(simulation = sim_34_size_cov, run.parallel = TRUE)
sim_35_size_cov <- 
  run.simulation(simulation = sim_35_size_cov, run.parallel = TRUE)
sim_41_size_cov <- 
  run.simulation(simulation = sim_41_size_cov, run.parallel = TRUE)
sim_42_size_cov <- 
  run.simulation(simulation = sim_42_size_cov, run.parallel = TRUE)
sim_43_size_cov <- 
  run.simulation(simulation = sim_43_size_cov, run.parallel = TRUE)
sim_44_size_cov <- 
  run.simulation(simulation = sim_44_size_cov, run.parallel = TRUE)
sim_45_size_cov <- 
  run.simulation(simulation = sim_45_size_cov, run.parallel = TRUE)
sim_51_size_cov <- 
  run.simulation(simulation = sim_51_size_cov, run.parallel = TRUE)
sim_52_size_cov <- 
  run.simulation(simulation = sim_52_size_cov, run.parallel = TRUE)
sim_53_size_cov <- 
  run.simulation(simulation = sim_53_size_cov, run.parallel = TRUE)
sim_54_size_cov <- 
  run.simulation(simulation = sim_54_size_cov, run.parallel = TRUE)
sim_55_size_cov <- 
  run.simulation(simulation = sim_55_size_cov, run.parallel = TRUE)
```

```{r simulation results}
# Display a histogram of the estimates of abundance
#use.max.reps = TRUE
sim_11_standard_summary <- summary(sim_11_standard, description.summary = FALSE)
sim_12_standard_summary <- summary(sim_12_standard, description.summary = FALSE)
sim_13_standard_summary <- summary(sim_13_standard, description.summary = FALSE)
sim_14_standard_summary <- summary(sim_14_standard, description.summary = FALSE)
sim_15_standard_summary <- summary(sim_15_standard, description.summary = FALSE)
sim_21_standard_summary <- summary(sim_21_standard, description.summary = FALSE)
sim_22_standard_summary <- summary(sim_22_standard, description.summary = FALSE)
sim_23_standard_summary <- summary(sim_23_standard, description.summary = FALSE)
sim_24_standard_summary <- summary(sim_24_standard, description.summary = FALSE)
sim_25_standard_summary <- summary(sim_25_standard, description.summary = FALSE)
sim_31_standard_summary <- summary(sim_31_standard, description.summary = FALSE)
sim_32_standard_summary <- summary(sim_32_standard, description.summary = FALSE)
sim_33_standard_summary <- summary(sim_33_standard, description.summary = FALSE)
sim_34_standard_summary <- summary(sim_34_standard, description.summary = FALSE)
sim_35_standard_summary <- summary(sim_35_standard, description.summary = FALSE)
sim_41_standard_summary <- summary(sim_41_standard, description.summary = FALSE)
sim_42_standard_summary <- summary(sim_42_standard, description.summary = FALSE)
sim_43_standard_summary <- summary(sim_43_standard, description.summary = FALSE)
sim_44_standard_summary <- summary(sim_44_standard, description.summary = FALSE)
sim_45_standard_summary <- summary(sim_45_standard, description.summary = FALSE)
sim_51_standard_summary <- summary(sim_51_standard, description.summary = FALSE)
sim_52_standard_summary <- summary(sim_52_standard, description.summary = FALSE)
sim_53_standard_summary <- summary(sim_53_standard, description.summary = FALSE)
sim_54_standard_summary <- summary(sim_54_standard, description.summary = FALSE)
sim_55_standard_summary <- summary(sim_55_standard, description.summary = FALSE)


sim_11_size_cov_summary <- summary(sim_11_size_cov, description.summary = FALSE)
sim_12_size_cov_summary <- summary(sim_12_size_cov, description.summary = FALSE)
sim_13_size_cov_summary <- summary(sim_13_size_cov, description.summary = FALSE)
sim_14_size_cov_summary <- summary(sim_14_size_cov, description.summary = FALSE)
sim_15_size_cov_summary <- summary(sim_15_size_cov, description.summary = FALSE)
sim_21_size_cov_summary <- summary(sim_21_size_cov, description.summary = FALSE)
sim_22_size_cov_summary <- summary(sim_22_size_cov, description.summary = FALSE)
sim_23_size_cov_summary <- summary(sim_23_size_cov, description.summary = FALSE)
sim_24_size_cov_summary <- summary(sim_24_size_cov, description.summary = FALSE)
sim_25_size_cov_summary <- summary(sim_25_size_cov, description.summary = FALSE)
sim_31_size_cov_summary <- summary(sim_31_size_cov, description.summary = FALSE)
sim_32_size_cov_summary <- summary(sim_32_size_cov, description.summary = FALSE)
sim_33_size_cov_summary <- summary(sim_33_size_cov, description.summary = FALSE)
sim_34_size_cov_summary <- summary(sim_34_size_cov, description.summary = FALSE)
sim_35_size_cov_summary <- summary(sim_35_size_cov, description.summary = FALSE)
sim_41_size_cov_summary <- summary(sim_41_size_cov, description.summary = FALSE)
sim_42_size_cov_summary <- summary(sim_42_size_cov, description.summary = FALSE)
sim_43_size_cov_summary <- summary(sim_43_size_cov, description.summary = FALSE)
sim_44_size_cov_summary <- summary(sim_44_size_cov, description.summary = FALSE)
sim_45_size_cov_summary <- summary(sim_45_size_cov, description.summary = FALSE)
sim_51_size_cov_summary <- summary(sim_51_size_cov, description.summary = FALSE)
sim_52_size_cov_summary <- summary(sim_52_size_cov, description.summary = FALSE)
sim_53_size_cov_summary <- summary(sim_53_size_cov, description.summary = FALSE)
sim_54_size_cov_summary <- summary(sim_54_size_cov, description.summary = FALSE)
sim_55_size_cov_summary <- summary(sim_55_size_cov, description.summary = FALSE)

histogram.N.ests(sim_33_standard)
histogram.N.ests(sim_33_size_cov)
```

```{r bias standard summary}
standard_summary_bias <- c(
abs(sim_11_standard_summary@individuals$N$percent.bias), abs(sim_12_standard_summary@individuals$N$percent.bias),
abs(sim_13_standard_summary@individuals$N$percent.bias),
abs(sim_14_standard_summary@individuals$N$percent.bias),
abs(sim_15_standard_summary@individuals$N$percent.bias),
abs(sim_21_standard_summary@individuals$N$percent.bias),
abs(sim_22_standard_summary@individuals$N$percent.bias),
abs(sim_23_standard_summary@individuals$N$percent.bias),
abs(sim_24_standard_summary@individuals$N$percent.bias),
abs(sim_25_standard_summary@individuals$N$percent.bias),
abs(sim_31_standard_summary@individuals$N$percent.bias),
abs(sim_32_standard_summary@individuals$N$percent.bias),
abs(sim_33_standard_summary@individuals$N$percent.bias),
abs(sim_34_standard_summary@individuals$N$percent.bias),
abs(sim_35_standard_summary@individuals$N$percent.bias),
abs(sim_41_standard_summary@individuals$N$percent.bias),
abs(sim_42_standard_summary@individuals$N$percent.bias),
abs(sim_43_standard_summary@individuals$N$percent.bias),
abs(sim_44_standard_summary@individuals$N$percent.bias),
abs(sim_45_standard_summary@individuals$N$percent.bias),
abs(sim_51_standard_summary@individuals$N$percent.bias),
abs(sim_52_standard_summary@individuals$N$percent.bias),
abs(sim_53_standard_summary@individuals$N$percent.bias),
abs(sim_54_standard_summary@individuals$N$percent.bias),
abs(sim_55_standard_summary@individuals$N$percent.bias)
)

#ROW THEN COLUMN

standard_summary_bias.data <- 
  matrix(standard_summary_bias, nrow = 5, ncol = 5, byrow = TRUE)

standard_summary_bias.data_melt <- melt(standard_summary_bias.data)

standard_model_output <- ggplot(standard_summary_bias.data_melt, aes(X2, X1)) +
  geom_tile(aes(fill = value)) +
  labs(y = "Beta 0", x = "Beta 1", title = "Standard Model Bias")
standard_model_output

# scale_x_continuous(limits = c(0.052, 0.056), breaks = seq(0.052, 0.056, 5)) +
#   scale_y_continuous(limits = c(4, 8), breaks = seq(4, 8, 5)) +

```

```{r bias size cov summary}
size_cov_summary_bias <- c(
abs(sim_11_size_cov_summary@individuals$N$percent.bias), abs(sim_12_size_cov_summary@individuals$N$percent.bias),
abs(sim_13_size_cov_summary@individuals$N$percent.bias),
abs(sim_14_size_cov_summary@individuals$N$percent.bias),
abs(sim_15_size_cov_summary@individuals$N$percent.bias),
abs(sim_21_size_cov_summary@individuals$N$percent.bias),
abs(sim_22_size_cov_summary@individuals$N$percent.bias),
abs(sim_23_size_cov_summary@individuals$N$percent.bias),
abs(sim_24_size_cov_summary@individuals$N$percent.bias),
abs(sim_25_size_cov_summary@individuals$N$percent.bias),
abs(sim_31_size_cov_summary@individuals$N$percent.bias),
abs(sim_32_size_cov_summary@individuals$N$percent.bias),
abs(sim_33_size_cov_summary@individuals$N$percent.bias),
abs(sim_34_size_cov_summary@individuals$N$percent.bias),
abs(sim_35_size_cov_summary@individuals$N$percent.bias),
abs(sim_41_size_cov_summary@individuals$N$percent.bias),
abs(sim_42_size_cov_summary@individuals$N$percent.bias),
abs(sim_43_size_cov_summary@individuals$N$percent.bias),
abs(sim_44_size_cov_summary@individuals$N$percent.bias),
abs(sim_45_size_cov_summary@individuals$N$percent.bias),
abs(sim_51_size_cov_summary@individuals$N$percent.bias),
abs(sim_52_size_cov_summary@individuals$N$percent.bias),
abs(sim_53_size_cov_summary@individuals$N$percent.bias),
abs(sim_54_size_cov_summary@individuals$N$percent.bias),
abs(sim_55_size_cov_summary@individuals$N$percent.bias))

#ROW THEN COLUMN

size_cov_summary_bias.data <- 
  matrix(size_cov_summary_bias, nrow = 5, ncol = 5, byrow = TRUE)

size_cov_summary_bias.data_melt <- melt(size_cov_summary_bias.data)

size_cov_model_output <- ggplot(size_cov_summary_bias.data_melt, aes(X2, X1)) +
  geom_tile(aes(fill = value)) +
  labs(y = "Beta 0", x = "Beta 1", title = "Size Covariate Model Bias")
size_cov_model_output

```



EOF